```{r}
library(dplyr)
library(tidyr)
library(curl)
library(reshape2)
```

```{r}
filename <- "getdata_projectfiles.zip"
```
## Download and unzip the dataset:
```{r}
if(!file.exists(filename)){
  fileUrl <- "https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip"
  download.file(fileUrl, filename, method = "curl")
}
if(!file.exists("UCI HAR Dataset")){
  unzip(filename)
}
# recording the date for downloading datasets
downloadedData <- date()
downloadedData
list.files()
```
# Load activity labels + features
```{r}
setwd("C:/Users/hanwe/Documents/Datasciencecoursera/Getting_and_Cleaning_Course/Project/UCI HAR Dataset")
# read train data
train_data <- read.table("train/X_train.txt")
train_label <- read.table("train/y_train.txt")
train_subject <- read.table("train/subject_train.txt")
# read test data
test_data <- read.table("test/X_test.txt")
test_label <- read.table("test/y_test.txt")
test_subject <- read.table("test/subject_test.txt")
```
# read feature file
```{r}
variable_names <- read.table("./UCI HAR Dataset/features.txt")
variable_names <- tbl_df(variable_names)
head(variable_names)
```
# read activity_labels file
```{r}
activity_labels <- read.table("./UCI HAR Dataset/activity_labels.txt")
activity_labels <- tbl_df(activity_labels)
tail(activity_labels)
```
# to create a uniform data set by two datasets for the training data and its corresponding labels, and two datasets for the test #data and its corresponding labels
```{r}
col_names <- readLines("./UCI HAR Dataset/features.txt")
colnames(train_data)<-make.names(col_names)
colnames(test_data)<-make.names(col_names)
colnames(train_subject) <- "subjectID"
colnames(test_subject) <- "subjectID"
colnames(train_label)<-"activityID"
colnames(test_label)<-"activityID"
colnames(activity_labels) <- c("activityID", "activityType")
```

# 1. Merges the training and the test sets to create one data set.
```{r}
train_total <- cbind(train_subject,train_label,train_data)
test_total <- cbind(test_subject,test_label,test_data)
final_data <- rbind(train_total, test_total)
final_data <- tbl_df(final_data)
head(final_data)
```
# 2.Extracts only the measurements on the mean and standard deviation for each measurement.
```{r}
sub_data <- final_data %>% select(contains("subjectID"),contains("activityID"),contains(".mean."),contains(".std."))
write.table(sub_data, "Mean_And_STD_For_Measurement.txt")
head(sub_data)
```
# 3.Uses descriptive activity names to name the activities in the data set
```{r}
final_data$activityID[final_data$activityID == 1] <- "walking"
final_data$activityID[final_data$activityID == 2] <- "walking upstairs"
final_data$activityID[final_data$activityID == 3] <- "walking downstairs"
final_data$activityID[final_data$activityID == 4] <- "sitting"
final_data$activityID[final_data$activityID == 5] <- "standing"
final_data$activityID[final_data$activityID == 6] <- "laying"
head(final_data)
tail(final_data)
sub_data$activityID[sub_data$activityID == 1] <- "walking"
sub_data$activityID[sub_data$activityID == 2] <- "walking upstairs"
sub_data$activityID[sub_data$activityID == 3] <- "walking downstairs"
sub_data$activityID[sub_data$activityID == 4] <- "sitting"
sub_data$activityID[sub_data$activityID == 5] <- "standing"
sub_data$activityID[sub_data$activityID == 6] <- "laying"
head(sub_data)
tail(sub_data)
```
# 4.Appropriately labels the data set with descriptive variable names.
```{r}
names(sub_data) <- gsub("Acc", "Accelerometer", fixed = TRUE, names(sub_data)) 
names(sub_data)<-gsub("Gyro", "Gyroscope", fixed = TRUE,names(sub_data))
names(sub_data)<-gsub("BodyBody", "Body", fixed = TRUE,names(sub_data))
names(sub_data)<-gsub("Mag", "Magnitude", fixed = TRUE,names(sub_data))
names(sub_data)<-gsub("^t", "Time", fixed = TRUE,names(sub_data))
names(sub_data)<-gsub("^f", "Frequency", fixed = TRUE,names(sub_data))
names(sub_data)<-gsub("tBody", "TimeBody", fixed = TRUE,names(sub_data))
names(sub_data)<-gsub("-mean()", "Mean", fixed = TRUE,names(sub_data), ignore.case = TRUE)
names(sub_data)<-gsub("-std()", "STD", fixed = TRUE,names(sub_data), ignore.case = TRUE)
names(sub_data)<-gsub("-freq()", "Frequency", fixed = TRUE,names(sub_data), ignore.case = TRUE)
names(sub_data)<-gsub("angle", "Angle", fixed = TRUE,names(sub_data))
names(sub_data)<-gsub("gravity", "Gravity", fixed = TRUE,names(sub_data))
head(final_data)
```
# 5.From the data set in step 4, creates a second, independent tidy data set with the average of each variable for each activity and each subject.
```{r}
TidyData <- sub_data %>%
    group_by(subjectID,activityID) %>%
    summarise_all(funs(mean))
write.table(TidyData, "C:/Users/hanwe/Documents/Datasciencecoursera/Getting_and_Cleaning_Course/Project/TidyData.txt", row.name=FALSE)
```

```{r}
str(TidyData)
```

```{r}
print(TidyData)
```
